% Jason R. Blevins - Curriculum Vitae
%
% Copyright (C) 2004-2010 Jason R. Blevins
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely.  No attribution is
% required in any resulting documents.  I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[10pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Fonts
\usepackage[T1]{fontenc}
\usepackage[bitstream-charter]{mathdesign}
\usepackage[scaled=0.85]{beramono}

% Set your name here
\def\name{Jason R. Blevins}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, econometrics, industrial organization,
    applied microeconomics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}[t]{0.5\textwidth}
  Department of Economics \\
  The Ohio State University \\
  410 Arps Hall \\
  1945 N High Street \\
  Columbus, OH 43210
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
  Office: (614) 292-5588 \\
  Mobile: (919) 624-4756 \\
  Fax: (614) 292-3906 \\
  Email: \texttt{blevins.141@osu.edu} \\
  Homepage: \texttt{http://jblevins.org/} \\
\end{minipage}

\section*{Current Position}

Assistant Professor, Department of Economics, The Ohio State University

\section*{Education}

\begin{itemize}

  % May 14, 2004
  \item B.S. Applied Mathematics, North Carolina State University, 2004.

    \begin{itemize}

    \item \textit{Minors:}
      Computer Science and Economics.

    \item \textit{Honors:}
      \textit{Summa Cum Laude}, Phi Beta Kappa.

    \item \textit{Advanced study:}
      Budapest Semesters in Mathematics, Fall 2002.

    \end{itemize}

  % May 14, 2006
  \item M.A. Economics, Duke University, 2006.

  % May 16, 2010
  \item Ph.D. Economics, Duke University, 2010.

    \begin{itemize}

    \item \textit{Dissertation:}
      Essays in Industrial Organization and Econometrics.

    \item \textit{Committee:}
      Han Hong (co-chair), Shakeeb Khan (co-chair),
      Paul Ellickson, and Andrew Sweeting.

    \end{itemize}

\end{itemize}

\section*{Academic Experience}

\subsection*{North Carolina State University,
  Department of Mathematics}

\begin{itemize}

\item Mathematics Tutor, Academic Support Program for Student Athletes,
  Summer 2001.

\item Research Assistant, Moody Chu and Robert Funderlic,
  Spring 2003--Fall 2004.

\end{itemize}

\subsection*{Colorado School of Mines,
  Department of Mathematical and Computer Sciences}

\begin{itemize}

\item Research Assistant, Willy Hereman, Summer 2002.

\end{itemize}

\subsection*{Duke University, Department of Economics}

\begin{itemize}

\item Research Assistant, Jacob Vigdor, Summer 2005--Summer 2006.

\item Teaching Assistant, Ph.D. Microeconomic Analysis, Thomas Nechyba,
  Fall 2005.

\item Teaching Assistant, Ph.D. Game Theory, Curtis Taylor,
  Spring 2006.

\item Instructor, Microeconomics Qualifier Camp, Summer 2006.

\item Research Assistant, Han Hong, Fall 2006--Spring 2007.

\item Research Assistant, Aprajit Mahajan and Alessandro Tarozzi,
  October--November 2006, March--June 2007.

\item Research Assistant, Shakeeb Khan and Christopher Timmins,
  March--June 2007.

\item Teaching Assistant, Ph.D. Econometrics II, Shakeeb Khan,
  Spring 2007.

\item Research Assistant, Peter Arcidiacono, Patrick Bayer,
  and Paul Ellickson, Fall 2007--Spring 2009.

\item Research Assistant, Shakeeb Khan, Fall 2009--Spring 2010.

\item Research Assistant, Aprajit Mahajan, July--September 2009.

\end{itemize}

\subsection*{The Ohio State University, Department of Economics}

\begin{itemize}

\item Assistant Professor, July 2010--Present.

\end{itemize}

\section*{Research}

\subsection*{Working Papers}

\begin{itemize}

\item \href{http://jblevins.org/research/smcdmm}{Sequential Monte Carlo Methods for Estimating Dynamic Microeconomic Models}.

\item \href{http://jblevins.org/research/lnlls}{Local NLLS Estimation of Semiparametric Binary Choice Models},
  with Shakeeb Khan.

\item \href{http://jblevins.org/research/dfbr}{Distribution-Free Estimation of Heteroskedastic Binary Response Models in Stata},
  with Shakeeb Khan.

\item \href{http://jblevins.org/research/dcident}{Nonparametric Identification of Dynamic Games with Discrete and Continuous Choices}.

\item \href{http://jblevins.org/research/abbe}{Estimation of Dynamic Discrete Choice Models in Continuous Time},
  with Peter Arcidiacono, Patrick Bayer, and Paul Ellickson.

\item \href{http://jblevins.org/research/panel}{Partial Identification and Inference in Binary Choice and Duration Panel Data Models}.

\end{itemize}

\subsection*{Publications}

\begin{itemize}

\item Blevins, Jason~R. (2009).
  \href{http://jblevins.org/research/generic-list}{A Generic Linked List Implementation in Fortran 95}.
  \textit{ACM Fortran Forum} 28(3), 2--7.

\end{itemize}

\subsection*{Scientific Software}

\begin{itemize}

\item \href{http://jblevins.org/research/pdest}{PDESolutionTester},
  A Mathematica program for the symbolic verification of exact solutions
  of nonlinear partial differential equations,
  with Jeff Heath and Willy Hereman (2002).

\item \href{http://jblevins.org/research/dfbr}{DFBR},
  A Stata program for distribution-free estimation of heteroskedastic
  binary response models,
  with Shakeeb Khan (2009).

\end{itemize}

\section*{Conference and Seminar Presentations}

\begin{itemize}

\item \href{http://jblevins.org/research/smcdmm}{Sequential Monte Carlo Methods for Estimating Dynamic Microeconomic Models}

  \begin{itemize}

  \item ERID Conference on Identification Issues in Economics,
    Duke University, October 3, 2008.

  \end{itemize}

\item \href{http://jblevins.org/research/panel}{Partial Identification and Inference in Binary Choice and Duration
    Panel Data Models}

  \begin{itemize}

  \item Triangle Econometrics Conference, Research Triangle Park, NC,
    December 4, 2009.

  \item University of Pittsburgh, Department of Economics,
    January 15, 2010.

  \item University of Illinois at Urbana-Champaign, Department of Economics,
    February 16, 2010.

  \end{itemize}

\item \href{http://jblevins.org/research/abbe}{Estimation of Dynamic Discrete Choice Models in Continuous Time}

  \begin{itemize}

  \item The Ohio State University, Department of Economics,
    January 21, 2010.

  \item University of Western Ontario, Department of Economics,
    January 26, 2010.

  \end{itemize}

\end{itemize}

\section*{Professional Activities}

\begin{itemize}

\item Member, Econometric Society, 2006--Present.

\item Member, American Economic Association, 2010--Present.

\item Referee for:

  \begin{itemize}
  \item \textit{Economic Inquiry} % 2008 (1)
  \item \textit{Journal of Business and Economic Statistics} % 2009 (1)
  \item \textit{Journal of Econometrics} % 2009 (1)
  \item \textit{Scandinavian Journal of Statistics} % 2009 (1)
  \end{itemize}

\end{itemize}

\section*{Conferences and Workshops Attended}

\begin{itemize}

\item SIAM Conference on Applied Linear Algebra,
  The College of William \& Mary,
  July 15--19, 2003.

\item Institute on Computational Economics,
  Argonne National Laboratory,
  July 17--21, 2006.

\item North American Summer Meetings of the Econometric Society,
  Duke University,
  June 21--24, 2007.

\item ERID Conference on Identification,
  Duke University,
  October 3--4, 2008.

\item Cowles Foundation Conference on Applications of Structural Microeconomics,
  Yale University,
  June 24--25, 2009.

\item Triangle Econometrics Conference,
  Research Triangle Park, NC,
  December 4, 2009.

\item AEA Annual Meeting,
  Atlanta, GA, January 3--5, 2010.

\end{itemize}

\section*{Honors, Awards, \& Fellowships}

\begin{itemize}

\item Dean's List, North Carolina State University, 2000--2004.

\item Golden Key International Honour Society, 2002.

\item Phi Kappa Phi, 2002.

\item NSF Research Experiences for Undergraduates,
  Colorado School of Mines, 2002.

\item Pi Mu Epsilon, National Mathematics Honor Society, 2003.

\item Phi Beta Kappa, Zeta of North Carolina, 2003.

\item Omicron Delta Epsilon, International Economics Honor Society, 2004.

\item Undergraduate Research Award, North Carolina State University, 2004.

\item Outstanding Teaching Assistant Award, Duke University, 2006.

\item Institute on Computational Economics
  Fellow, University of Chicago, 2006.

\item Summer Research Fellowship, Duke University, 2007.

\item Summer Research Fellowship, Duke University, 2008.

\end{itemize}

\section*{Miscellaneous}

\begin{itemize}

  \item \textit{Security Clearance:} Special Sworn Status, U.S. Census Bureau.

\end{itemize}

\bigskip

% Footer
\begin{center}
  \begin{small}
    Last updated: \today
  \end{small}
\end{center}

\end{document}

